Group 1: Tennis 

### 2019-12-11 Group1Prez.Rmd
Updated

```{r setup, include=FALSE, warning=FALSE}
source("funs.R")
library(knitr)
options(kableExtra.latex.load_packages = FALSE) 
library(kableExtra)
library(tidyverse)
set.seed(400)
```

@@

## Game of Tennis 
![](tennis-scoring.jpg){ width=85% }\

>>>>

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("funs.R")
library(knitr)
options(kableExtra.latex.load_packages = FALSE) 
library(kableExtra)
library(tidyverse)
set.seed(400)
```

@@

## Game of Tennis 
![](Scoring.jpg){ width=85% }\
